### 2019-07-16 reports/thesis/chapters/2_dataCollection.tex
ANOVA write up

A variation of the shading correction which uses only the black and white image such that $\mathfrak{P}=\left\{0,P_\text{proj}\right\}$ shall be known as BW shading correction.

@@

The BW shading corrected black image looks very uniform but there is some structure in the linear shading correction. By giving linear shading correction various greyscale projections, it tried to generalise to a range of powers and thus may struggle at shading correcting the black and white images.

@@

@@

% \begin{figure}
%   \centering
%   \centerline{
%     \begin{subfigure}[b]{0.49\textwidth}
%       \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_blackFft_null.eps}
%       \caption{No shading correction}
%     \end{subfigure}
%     \begin{subfigure}[b]{0.49\textwidth}
%       \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_blackFft_bw.eps}
%       \caption{BW shading correction}
%     \end{subfigure}
%   }
%   \begin{subfigure}[b]{0.49\textwidth}
%     \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_blackFft_linear.eps}
%     \caption{Linear shading correction}
%   \end{subfigure}
%   \caption{Fourier transform on the black image before and after shading correction. The colour scale is in arbitrary units and range between 0 to 255.}
%   \label{fig:data_fft}
% \end{figure}

@@

Figure \ref{fig:data_AbsNoFilter} shows the data. Shading correction is done via the following. It requires calibration images, they are projections of nothing at different powers. For each calibration image, calculate the within image mean. For each pixel, do a linear regression of the within image mean versus the grey value for different powers: bw shading correction uses only the black and max power calibration images, linear shading correction uses all calibration images. The regression maps the uncorrected grey value ($x$) to the shading corrected grey value ($y$) for this particular pixel.

An example is shown in Figure \ref{fig:data_shadingCorrectionExample_gainMap}. In Figure \ref{fig:data_shadingCorrectionExample_gainMap} a), 3 random pixels were used to demonstrate the regression. The gradient of the regression for all pixels are shown in Figure \ref{fig:data_shadingCorrectionExample_gainMap} b).

The gain is actually the sensitivity so it should be a plot of the grey value versus the power, this is shown in Figure \ref{fig:data_shadingCorrectionExample_gain}. However this is similar to the linear regression done for shading correction.

In the black image, I've noticed the vertical read-out structure can be seen. This can be done by plotting the grey value down a column as shown in Figure \ref{fig:data_oddEven}. In particular, the grey value jumps up and down at every pixel, this is seen by plotting the same profile curve but for every odd and even $y$. Shading correction corrects this because the black image has information on the odd/even structure which is then fed into the shading correction.

An autocorrelation plot could be plotted, but it's easier to do a Fourier transform, this is shown in Figure \ref{fig:data_fft}.

No read-out structure can be seen horizontally, see Figure \ref{fig:data_oddEvenX}. Panel structure can be seen however.

>>>>

A variation of the shading correction which uses only the black and white image such that $\mathfrak{P}=\left\{0,P_\text{proj}\right\}$ shall be known as black/white (BW) shading correction.

@@

The BW shading corrected black and white image looks very uniform but there is some structure in the linear shading correction. By giving linear shading correction various greyscale projections, it tried to generalise to a range of powers and thus may struggle at shading correcting the black and white images.

@@

\begin{figure}
  \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_white_bw.eps}
      \caption{BW shading correction}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_white_linear.eps}
      \caption{Linear shading correction}
    \end{subfigure}
  }
  \caption{The \texttt{AbsNoFilter} white image after shading correction.}
  \label{fig:data_shadingCorrectionExample_white}
\end{figure}

@@

@@

An experiment was conducted to quantify the performance of the different types of shading correction. Applying shading correction on the greyscale image should remove effects from the panels and the spot, leaving a flat noisy image with no spatial structure. The variance within a pixel and across replications should be similar to between pixels within a replication if the shading correction flatten the greyscale images.

In the \texttt{AbsNoFilter} dataset, there are 20 replicated greyscale images for each power. One randomly selected replication from each power was assigned to the training set and used to calibrate the shading correction. The remaining images was assigned to the test set and the shading correction was applied to each image.

For each power, the within and between pixel variance was calculated. Let $U_{x,y}^{(j)}(P)$ be the shading corrected greyscale image in the test set with power $P$ for $j=1,2,\cdots,n$ replicates. The within and between pixel variance are
\begin{equation}
s_\mathrm{w}^2(P)=\dfrac{1}{WH(n-1)}
  \sum_{x=1}^{W}\sum_{y=1}^{H}\sum_{j=1}^{n}
  \left(
    U_{x,y}^{(j)}(P) - \overline{U}_{x,y}(P)
  \right)^2
\end{equation}
and
\begin{equation}
s_\mathrm{b}^2(P)=\dfrac{1}{WH-1}
  \sum_{x=1}^{W}\sum_{y=1}^{H}
  \left(
    \overline{U}_{x,y}(P) - \overline{U}(P)
  \right)^2
\end{equation}
respectively where
\begin{equation}
  \overline{U}_{x,y}(P) = \dfrac{1}{n}\sum_{j=1}^{n}U_{x,y}^{(j)}(P)
\end{equation}
and
\begin{equation}
  \overline{U}(P) = \dfrac{1}{WH}\sum_{x=1}^{W}\sum_{y=1}^{H}\overline{U}_{x,y}(P)
  \ .
\end{equation}
In this specific experiment, $W=2000$, $H=2000$ and $n=19$. The $F$ statistic is
\begin{equation}
F(P)=\dfrac{s_\mathrm{b}^2(P)}{s_\mathrm{w}^2(P)}
\end{equation}
and should be about one if the within and between pixel variances are similar. The experiment was repeated 100 times by reallocating the training and test set.

\begin{figure}
  \centering
  \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsNoFilter_null.eps}
      \caption{No shading correction}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsNoFilter_bw.eps}
      \caption{BW shading correction}
    \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsNoFilter_linear.eps}
      \caption{Linear shading Correction}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsNoFilter_FStatistic.eps}
      \caption{$F$ statistic}
    \end{subfigure}
  }
  \caption{One randomly selected greyscale image from each power was used to train the shading correction which was then applied to the remaining of the greyscale images. The within and between pixel variance were estimated and used to calculate a $F$ statistic for each power. The box plots represent the 100 repeats. The experiment was repeated by reselecting the greyscale image used for training the shading correction.}
  \label{fig:data_anova}
\end{figure}

The results are shown in Figure \ref{fig:data_anova} and shows that with shading correction, the within and between pixel variance become more similar. A difference between BW and linear shading correction is that for the black image, the $F$ statistic is better for BW compared to linear shading correction. For the rest of the powers, linear shading correction outperforms BW shading correction. This shows that linear shading correction generalise to powers between the black and white image. Since beam extinction is avoided, black grey values in the obtained projection should not be possible. As a result, the linear shading correction is recommended for its good performance for various powers.

Using the $F$ test from ANOVA was found to be too strict in this experiment. Under the hypothesis that the grey values all have the same mean and assume they are Normally distributed and i.i.d., then $F(P)\sim F_{WH-1,WH(n-1)}$. In this experiment, the 5\% critical value is 1.001 to 3 decimal places. This may be due to the grey values of the greyscale images not satisfying the assumptions for the $F$ test, for example they may not be i.i.d.
